Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2016-07-09 manuscript/manuscript_pve.Rmd
added intro point

#Introduction
The source-sink limitation paradigm for plant growth argues that growth may be limited either by source activity, i.e. the amount of carbon that the plants are able to take up through photosynthesis, or by sink strength, i.e. the amount of carbon that the plants are able to utilize in growth.  To be able to predict plant growth responses to environmental change, we need models that can account for both source and sink limitation.

@@

```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize.R")
```  
**Figure 6**. (a) Total C mass of harvested seedlings versus modelled net leaf carbon gain over 120 days. The dashed black line shows the 1:1 line and the dotted blue line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling. (b) Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.

>>>>

#Introduction
The source-sink limitation paradigm for plant growth argues that growth may be limited either by source activity, i.e. the amount of carbon that the plants are able to take up through photosynthesis, or by sink strength, i.e. the amount of carbon that the plants are able to utilize in growth. This debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role; @korner2015paradigm]. To be able to predict plant growth responses to environmental change, we need models that can account for both source and sink limitation.

@@

```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize.R")
```  
**Figure 6**. (a) Total carbon mass of harvested seedlings versus modelled net leaf carbon gain over 120 days. The dashed black line shows the 1:1 line and the dotted blue line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling. (b) Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.
